LAGOS lake depth

### 2020-02-11 figures/00_qa.Rmd
create a qa plot for mean depth

@@

names(lg$locus$locus_link$l)
res <- dt %>% 
  left_join(
    dplyr::select(lg$locus$locus_link, lagoslakeid, lagosne_lagoslakeid)) %>%
  left_join(
    dplyr::select(lg$locus$locus_characteristics, 
                  lagoslakeid, lake_totalarea_ha)) %>%
  dplyr::filter(!is.na(lagosne_lagoslakeid)) %>%
  dplyr::filter(lagoslakeid == lagosne_lagoslakeid) %>%
  dplyr::filter(!is.na(lake_maxdepth_m)) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::select(lagoslakeid, lagosne_lagoslakeid, lake_waterarea_ha, 
                lake_totalarea_ha, lake_maxdepth_m) %>%
  left_join(dplyr::select(lg_ne$locus, lagosne_lagoslakeid = lagoslakeid, 
                          lake_area_ha)) %>%
  mutate(diff = lake_area_ha - lake_waterarea_ha) %>%
  arrange(desc(diff))

>>>>

```{r lgnemanual-bathy-meandepth}
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE)
dt_sub <- dt %>%
  dplyr::filter(
    lagos_effort %in% c("LAGOSNE", "bathymetry", "manual") &
    !is.na(lake_meandepth_m)) %>%
  dplyr::select(lagoslakeid, lake_state, lagos_effort, lake_meandepth_m) %>%
  tidyr::pivot_wider(names_from = lagos_effort, 
                     values_from = c(lake_meandepth_m)) %>%
  dplyr::filter(!is.na(bathymetry)) %>%
  mutate(combined = coalesce(manual, LAGOSNE)) %>%
  dplyr::filter(!is.na(combined))

(gg <- ggplot(data = dplyr::filter(dt_sub, !(lake_state %in% c("ME", "NH")))) +
  geom_text(aes(x = bathymetry, y = combined, color = lake_state, 
                 label = lagoslakeid)) +
  geom_abline(aes(intercept = 0, slope = 1)))

# plotly::ggplotly(gg)
```

@@

res <- dt %>% 
  left_join(
    dplyr::select(lg$locus$locus_link, lagoslakeid, lagosne_lagoslakeid)) %>%
  left_join(
    dplyr::select(lg$locus$locus_characteristics, 
                  lagoslakeid, lake_totalarea_ha)) %>%
  dplyr::filter(!is.na(lagosne_lagoslakeid)) %>%
  dplyr::filter(lagoslakeid == lagosne_lagoslakeid) %>%
  dplyr::filter(!is.na(lake_maxdepth_m)) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::select(lagoslakeid, lagosne_lagoslakeid, lake_waterarea_ha, 
                lake_totalarea_ha, lake_maxdepth_m) %>%
  left_join(dplyr::select(lg_ne$locus, lagosne_lagoslakeid = lagoslakeid, 
                          lake_area_ha)) %>%
  mutate(diff = lake_area_ha - lake_waterarea_ha) %>%
  arrange(desc(diff))
